Prediction of Drinking Water Treatment Process Chemical Doses

### 2025-12-17 FinalPaper_DSCI445_Group4.Rmd
final changes to paper

train <- RWAR_dosing %>% filter(Year %in% c(2018, 2019))
test  <- RWAR_dosing %>% filter(Year == 2020)
```
All predictors:
```{r}
model0 <- lm(FeCl_dose ~ mean_Temp + mean_pH + mean_Conductivity + mean_Turbidity + Temp_lag1 + Temp_lag2 + pH_lag1 + pH_lag2 + Cond_lag1 + Cond_lag2 + Turb_lag1 + Turb_lag2, data = train)

@@

Generate model results
```{r}
models <- list(

@@

}
  performance <- performance %>% arrange(RMSE)
```
Selecting the best RMSE:
```{r}
best_rmse <- min(performance$RMSE)
best_rmse
```
Display Plots of models' performance on test data:
```{r}
kable_table_pdf <- performance %>%
  # Use format = "latex" for PDF output
  kable("latex",
        booktabs = TRUE)

>>>>

train <- RWAR_dosing %>% filter(Year %in% c(2018, 2019))
test  <- RWAR_dosing %>% filter(Year == 2020)
```

```{r}
model0 <- lm(FeCl_dose ~ mean_Temp + mean_pH + mean_Conductivity + mean_Turbidity + Temp_lag1 + Temp_lag2 + pH_lag1 + pH_lag2 + Cond_lag1 + Cond_lag2 + Turb_lag1 + Turb_lag2, data = train)

@@

```{r}
models <- list(

@@

}
  performance <- performance %>% arrange(RMSE)
```

```{r}
best_rmse <- min(performance$RMSE)
```

```{r}
kable_table_pdf <- performance %>%
  # Use format = "latex" for PDF output
  kable("latex",
        booktabs = TRUE)
